FAIR fission track analysis with geochron@home

### 2025-10-03 geochron@home/manuscript/paper.tex
G@H manuscript ready for final round of internal review.

\begin{small}
  \input{../output/shortcrowdtable.txt}\\
\end{small}
\captionof{table}{Counts of fission tracks in the same ROIs of 25
  grains made by PV and 68 students. Only 20 students are shown due to
  space constraints; the full table is provided in the supplementary
  information.  Each student counted a subset of the grains. The
  grains are listed in increasing order of PV's counts. The last 3
  columns give, for each student, the number of grains counted $n_g$
  and the weighted mean $r_p = \sum\,w_i\,r_i/\sum\,w_i$ and standard
  deviation $s_p = \sqrt{\sum w_i\,(r_i-r_p)^2/(n_g − 1)}$
  where $r_i$ is the ratio of the student's count to PV's count for
  grain $i$ and $w_i$ is PV's count for grain $i$. ($r_p$ is the same
  as the ratio of the student's total count over the $n_g$ grains to
  PV's total count over the same grains.)  The students are listed in
  decreasing order of $r_p$. $r_m$ is the ratio of the students'
  median count per grain to PV's count.}
\label{tab:crowdtable}

@@

\noindent\begin{minipage}{.55\linewidth}
  \includegraphics[width=\linewidth]{stripchart.pdf}\medskip
\end{minipage}
\begin{minipage}{.45\linewidth}
\captionof{figure}{Dot plot of the data shown in
  Table~\ref{tab:crowdtable}, with the students' medians and PV's
  counts shown as yellow and blue triangles, respectively.
  \medskip}
  \label{fig:stripchart}
\end{minipage}

>>>>

\begin{small}
  \input{../output/shortcrowdtable.txt}\\
\end{small}
\captionof{table}{Counts of fission tracks in the same ROIs of 25
  grains made by PV and 68 students. Only 20 students are shown due to
  space constraints; the full table is provided in the GaHa.  Each
  student counted a subset of the grains. The grains are listed in
  increasing order of PV's counts. The last 3 columns give, for each
  student, the number of grains counted $n_g$ and the weighted mean
  $r_p = \sum\,w_i\,r_i/\sum\,w_i$ and standard deviation $s_p =
  \sqrt{\sum w_i\,(r_i-r_p)^2/(n_g − 1)}$ where $r_i$ is the ratio of
  the student's count to PV's count for grain $i$ and $w_i$ is PV's
  count for grain $i$. ($r_p$ is the same as the ratio of the
  student's total count over the $n_g$ grains to PV's total count over
  the same grains.)  The students are listed in decreasing order of
  $r_p$. $r_m$ is the ratio of the students' median count per grain to
  PV's count.}
\label{tab:crowdtable}

@@

\noindent\begin{minipage}{.55\linewidth}
  \includegraphics[width=\linewidth]{stripchart.pdf}\medskip
\end{minipage}
\begin{minipage}{.45\linewidth}
\captionof{figure}{Strip chart of the data shown in
  Table~\ref{tab:crowdtable}, with the students' medians and PV's
  counts shown as yellow and blue triangles, respectively.
  \medskip}
  \label{fig:stripchart}
\end{minipage}
